---
title: "Supervised methods for HEPG2"
author: "Martha Zuluaga"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

# 1. Environment
```{r environ, echo=TRUE, message=FALSE, warning=FALSE}
#2. Add libraries 
library(timeSeries)
library(reshape2)
library(cluster)
library(gplots)
library(ggfortify)
library(ggplot2)
library(tidyverse)
library(base)
library(graphics)
library(stats)
library(fBasics)
library(pvclust)
library(randomForest)
library(varSelRF)
library(dplyr)
```


# 2. loading the data 
First I call the data already transformed and scaled
```{r}
# all features

Aldrin.all <- read.csv("07,1 - Aldrin Todos cd normalizado2.csv")
DDT.all <- read.csv("07,1 - DDT Todos cd normalizado2.csv")
Endosulfan.all <- read.csv("07,1 - Endosulfan Todos cd normalizado2.csv")
Lindane.all <- read.csv("07,1 - Lindano Todos cd normalizado2.csv")
Mix.all <- read.csv("07,1 - Mezcla Todos cd normalizado2.csv")

# Unknown  features
Aldrin.u <- read.csv("07,2 -  Aldrin descononocidos cd normalizado2.csv")
DDT.u <- read.csv("07,2 -  DDT descononocidos cd normalizado2.csv")
Endosulfan.u <- read.csv("07,2 -  Endosulfan descononocidos cd normalizado2.csv")
Lindane.u <- read.csv("07,2 -  Lindano descononocidos cd normalizado2.csv")
Mix.u <- read.csv("07,2 -  Mezcla descononocidos cd normalizado2.csv")

# Identified metabolites
Aldrin.i <- read.csv("07,3 - Aldrin cononocidos cd normalizado2.csv")
DDT.i <- read.csv("07,3 - DDT cononocidos cd normalizado2.csv")
Endosulfan.i <- read.csv("07,3 - Endosulfan cononocidos cd normalizado2.csv")
Lindane.i <- read.csv("07,3 - Lindano cononocidos cd normalizado2.csv")
Mix.i <- read.csv("07,3 - Aldrin cononocidos cd normalizado2.csv")
```

# Class prediction: Random forest(supervised) Aldrin.all

```{r}
set.seed(42)
Aldrin.a <- Aldrin.all[,-1]
Aldrin.RF <- randomForest(x = Aldrin.a, y = Aldrin.all[, 1], ntree = 100, mtry = 300, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(Aldrin.a,Aldrin.all[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(Aldrin.RF)
```

```{r}
varImpPlot(Aldrin.RF, sort = TRUE)
```
##################################

# Class prediction: Random forest(supervised). DDT.all

```{r}
set.seed(142)
DDT.a <- DDT.all[,-1]
DDT.RF <- randomForest(x = DDT.a, y = DDT.all[, 1], ntree = 100, mtry = 300, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(DDT.a,DDT.all[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(DDT.RF)
```

```{r}
varImpPlot(DDT.RF, sort = TRUE)
```


###################################################################################################

# Class prediction: Random forest(supervised). Endosulfan

```{r}
set.seed(42)
Endosulfan.a <- Endosulfan.all[,-1]
Endosulfan.RF <- randomForest(x = Endosulfan.a, y = Endosulfan.all[, 1], ntree = 100, mtry = 300, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(Endosulfan.a,Endosulfan.all[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(Endosulfan.RF)
```

```{r}
varImpPlot(Endosulfan.RF, sort = TRUE)
```


######################################################################################################


# Class prediction: Random forest(supervised). Lindane

```{r}
set.seed(42)
Lindane.a <- Lindane.all[,-1]
Lindane.RF <- randomForest(x = Lindane.a, y = Lindane.all[, 1], ntree = 100, mtry = 300, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(Lindane.a, Lindane.all[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(Lindane.RF)
```

```{r}
varImpPlot(Lindane.RF, sort = TRUE)
```


#########################################################################################################


# Class prediction: Random forest(supervised). Mixture

```{r}
set.seed(42)
Mix.a <- Mix.all[,-1]
Mix.RF <- randomForest(x = Mix.a, y = Mix.all[, 1], ntree = 100, mtry = 300, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(Mix.a, Mix.all[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(Mix.RF)
```

```{r}
varImpPlot(Mix.RF, sort = TRUE)
```


########################################################################################################################################################################################################################



# Class prediction: Random forest(supervised) Unknown

```{r}
set.seed(42)
Aldrin.un <- Aldrin.u[,-1]
Aldrin.RF.un <- randomForest(x = Aldrin.un, y = Aldrin.u[, 1], ntree = 100, mtry = 200, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(Aldrin.un,Aldrin.u[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(Aldrin.RF.un)
```

```{r}
varImpPlot(Aldrin.RF.un, sort = TRUE)
```


##########################################################################################################

# Class prediction: Random forest(supervised) Unknown

```{r}
set.seed(42)
DDT.un <- DDT.u[,-1]
DDT.RF.un <- randomForest(x = DDT.un, y = DDT.u[, 1], ntree = 100, mtry = 200, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(DDT.un, DDT.u[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(DDT.RF.un)
```

```{r}
varImpPlot(DDT.RF.un, sort = TRUE)
```

#############################################

# Class prediction: Random forest(supervised) Unknown

```{r}
set.seed(42)
Endosulfan.un <- Endosulfan.u[,-1]
Endosulfan.RF.un <- randomForest(x = Endosulfan.un, y = Endosulfan.u[, 1], ntree = 100, mtry = 200, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(Endosulfan.un, Endosulfan.u[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(Endosulfan.RF.un)
```

```{r}
varImpPlot(Endosulfan.RF.un, sort = TRUE)
```


################################################


# Class prediction: Random forest(supervised) Unknown

```{r}
set.seed(42)
Lindane.un <- Lindane.u[,-1]
Lindane.RF.un <- randomForest(x = Lindane.un, y = Lindane.u[, 1], ntree = 100, mtry = 200, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(Lindane.un, Lindane.u[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(Lindane.RF.un)
```

```{r}
varImpPlot(Lindane.RF.un, sort = TRUE)
```

#########################################################################


# Class prediction: Random forest(supervised) Unknown

```{r}
set.seed(42)
Mix.un <- Mix.u[,-1]
Mix.RF.un <- randomForest(x = Mix.un, y = Mix.u[, 1], ntree = 100, mtry = 200, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(Mix.un, Mix.u[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(Mix.RF.un)
```

```{r}
varImpPlot(Mix.RF.un, sort = TRUE)
```

##################################
##################################
##################################


# Class prediction: Random forest(supervised) identified

```{r}
#set.seed(100)
Aldrin.id <- Aldrin.i[,-1]
Aldrin.RF.id <- randomForest(x = Aldrin.id, y = Aldrin.i[, 1], ntree = 100, mtry = 100, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(Aldrin.id, Aldrin.i[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(Aldrin.RF.id)
```

```{r}
VIP.Aldrin <- varImpPlot(Aldrin.RF.id, sort = TRUE, 10)
write.csv(VIP.Aldrin, "data/run1.csv")
```

----Run 153 Random Forest
```{r}
most_relevant <- data.frame(row.names = c("comp1", "comp2", "comp3", "comp4",
                                          "comp5", "comp6" ,"comp7", "comp8",
                                          "comp9", "comp10"),
                            stringsAsFactors = TRUE)
for (i in 1:153){
  # path <- paste("data/run", as.character(i), ".csv", sep = "") #Crear carpeta "data"
  Aldrin.id <- Aldrin.i[,-1]
  Aldrin.RF.id <- randomForest(x = Aldrin.id, y = Aldrin.i[, 1],
                               ntree = 100, mtry = 100,
                               importance = TRUE)
  VIP.Aldrin <- varImpPlot(Aldrin.RF.id, sort = TRUE, 10)
  
  df <- data.frame(VIP.Aldrin)
  df$name <- names(Aldrin.id)
  df <- arrange(df, desc(MeanDecreaseAccuracy, MeanDecreaseGini)) %>% 
    select(name)
  most_relevant[i] <- df[1:10,]
  # write.csv(df, path)  # guardar cada evaluación.
}
```

Contar ocurrencias.
```{r}
df_ocurrencias <- data.frame(table(unlist(most_relevant)),
                             stringsAsFactors = TRUE)
arrange(df_ocurrencias, desc(Freq))
```

###################################################



```{r}
set.seed(42)
DDT.id <- DDT.i[,-1]
DDT.RF.id <- randomForest(x =DDT.id, y = DDT.i[, 1], ntree = 100, mtry = 100, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(DDT.id, DDT.i[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(DDT.RF.id)
```

```{r}
varImpPlot(DDT.RF.id, sort = TRUE)
```

##########################################



```{r}
set.seed(42)
Endosulfan.id <- Endosulfan.i[,-1]
Endosulfan.RF.id <- randomForest(x = Endosulfan.id, y = Endosulfan.i[, 1], ntree = 100, mtry = 100, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(Endosulfan.id, Endosulfan.i[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(Endosulfan.RF.id)
```

```{r}
varImpPlot(Endosulfan.RF.id, sort = TRUE)
```

#########################################



```{r}
set.seed(42)
Lindane.id <- Lindane.i[,-1]
Lindane.RF.id <- randomForest(x = Lindane.id, y = Lindane.i[, 1], ntree = 100, mtry = 100, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(Lindane.id, Lindane.i[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(Lindane.RF.id)
```

```{r}
varImpPlot(Lindane.RF.id, sort = TRUE)
```

###############################



```{r}
set.seed(42)
Mix.id <- Mix.i[,-1]
Mix.RF.id <- randomForest(x = Mix.id, y = Mix.i[, 1], ntree = 100, mtry = 100, 
                     importance = TRUE)

```

Variable selection procedure
```{r}
SelMET<-varSelRF(Mix.id, Mix.i[,1], mtryFactor = 2 )
SelMET
```

#plots of the random forest
What feature will allow me to split the observations at hand in a way that the resulting groups are as different from each other as possible (and the members of each resulting subgroup are as similar to each other as possible)?
```{r}
plot(Mix.RF.id)
```

```{r}
varImpPlot(Mix.RF.id, sort = TRUE)
a <- varImpPlot(Mix.RF.id, sort = TRUE)
```

```{r}
write.csv(a, "VIP_Mix.csv")
```

